
# "PredictionAssignmentWriteup"
by Max Ehrlich

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set.

##Preprocessing

Loading data, deleting Parameters with less variance, deleting Parameters with character values, separating in test and train-data, standardize parameters, impute missing values, factorization of parameters

setwd("C:\\Users\\Maximilian\\Documents\\GitHub\\Practical-Machine-Learning-Prediction-Assignment-Writeup")
```{r}
library(caret)
X <- read.csv("pml-training.csv", stringsAsFactors=FALSE)
#delete variables with to less variance
X <- X[,-nearZeroVar(X)]
#Delete variables with character-Values
X <- X[,-c(2,5)]

inTrain <- createDataPartition(y=X$classe, p=0.6, list=FALSE)
training <- X[inTrain,]
testing <- X[-inTrain,]

#standardize variables
#knnImpute for replacing missing values
#pca for factorization
preObj <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
#create dataset for prediction
clean_data <- predict(preObj,training[,-length(training)])
```

##Model-building

using the train dataset for building a random forest
```{r}
#calculating RandomForest with train set
Predictor<-as.factor(training$classe)
# model <- train(clean_data,Predictor, method="rf")
# #predicting in the test set
# test <- predict(preObj, testing[,-length(testing)])
# #test model with confusion matrix
# confusionMatrix(testing$classe, predict(model,test))
```
calculating the model takes over 1 day, so I just uncommented this lines