
# "PredictionAssignmentWriteup"
by Max Ehrlich

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set.

##Preprocessing

Loading data, deleting Parameters with less variance, deleting Parameters with character values, separating in test and train-data, standardize parameters, impute missing values, factorization of parameters

setwd("C:\\Users\\Maximilian\\Documents\\GitHub\\Practical-Machine-Learning-Prediction-Assignment-Writeup")
```{r}
library(caret)
X <- read.csv("pml-training.csv", stringsAsFactors=FALSE)
#delete variables with to less variance
X <- X[,-nearZeroVar(X)]
#Delete variables with character-Values
X <- X[,-c(2,5)]

inTrain <- createDataPartition(y=X$classe, p=0.6, list=FALSE)
training <- X[inTrain,]
testing <- X[-inTrain,]

#standardize variables
#knnImpute for replacing missing values
#pca for factorization
preObj <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
#create dataset for prediction
clean_data <- predict(preObj,training[,-length(training)])
#create clean_data for testing
test_data <- predict(preObj,testing[,-length(testing)])
```

##Model-building

using the train dataset for building a random forest
```{r}
#calculating RandomForest with train set
Predictor<-as.factor(training$classe)
Predictor_test<-as.factor(testing$classe)

library(randomForest)
model <- randomForest(Predictor ~ ., data = clean_data, ntree = 250)

#predicting in the train set
predictions_train <- predict(model, newdata=clean_data)
#predicting in the test set
predictions_test <- predict(model, newdata=test_data)

#test model with confusion matrix (test and train)
confusionMatrix(predictions_train,Predictor)
confusionMatrix(predictions_test, Predictor_test)

```
The train_data has an accuracy of 100%, which is perfect.
The test_data gets an accuracy of 97.36% which is very good!!! This means, that the model not only works on the training model, but also on new data.

